% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Baorui Peng}

\basicInfo{
  (86) 18304539277 $\bullet$
  \href{mailto:baorui.pengcn@gmail.com}{baorui.pengcn@gmail.com} $\bullet$
}

\section{Education}
\datedsubsection{\textbf{\href{https://www.bjut.edu.cn/}{Beijing University of Technology}}, Beijing, China}{09/2019 -- 07/2023}
B.Eng. in Electronic \& Information Engineering, GPA: 3.46/4.2
\datedsubsection{\textbf{\href{https://www.ucd.ie/}{University College Dublin}}, Dublin, Ireland}{09/2019 -- 07/2023}
B.Eng. in Electronic \& Information Engineering, GPA: 3.48/4.2

\section{Research Experience}
\datedsubsection{Research on garbage classification technology based on deep learning}{09/2022 -- 07/2023}
\begin{itemize}
  \item Final report on professional engineering project   [Grade A]
  \item An instance segmentation model that introduces transfer learning in the Mask R-CNN model is proposed. More information is extracted from the image than using the Mask R-CNN model alone.
  \item The results are viewed from two perspectives, on the one hand comparing the speed of the two models to train the same dataset and on the other hand analysing the accuracy of the final results obtained by the two models.
  \item Key responsibilities: Data collection and cleaning, model training, paper writing
\end{itemize}

\section{Project Experience}
\datedsubsection{Exploring the value flow effect}{03/2021 -- 06/2022}
\begin{itemize}
  \item A novel framework CDKCL based on Kirchhoff's circuit laws designed to understand knowledge transfer in citation networks is presented.
  \item Key responsibilities: Designed a paper-to-paper dependency measurement framework. Calculate the comprehensive correlation using Kirchhoff's circuit law. Use MAG database to conduct empirical analysis on the field of artificial intelligence.
\end{itemize}
\datedsubsection{Beijing University of Technology Mathematical Modelling Competition}{04/2021 -- 06/2021}
\begin{itemize}
  \item Main work: Write reports, analyse and summarise data. Provide optimal printing solutions for different types of books with a view to obtaining the greatest possible sales revenue.
  \item Key responsibilities: According to the number of models, team members' speciality and competition time, allocate team tasks reasonably and supervise team members to hand over tasks. Data collection and cleaning, model training, paper writing.
\end{itemize}

\section{Work Experience}
\datedsubsection{\textbf{\href{https://www.tsinghua-zj.edu.cn/technology/engineering/chan-ye-tan-zhong-he-yan-jiu-zhong-xin-2}{Industrial Carbon Neutrality Research Center at Yangtze Delta Region Institute of Tsinghua University in Zhejiang}}}{China}
\datedsubsection{Research Assistant}{03/2024 -- Now}
\begin{itemize}
\item Focused study on energy conservation and emission reduction
\item Devised the design objectives and validation of designs through simulations and testings
\item Part of Design group in the team helping with various design decisions
\end{itemize}
\datedsubsection{\textbf{\href{https://bdic.bjut.edu.cn/}{Beijing-Dublin International College}}}{China}
\datedsubsection{Teaching Assistant}{09/2021 -- 07/2023}
\begin{itemize}
  \item Beijing University of Technology
  \item Key responsibilities: Answer students' questions during class, guide students to operate the corresponding experiments in lab classes, and correct students' homework and lab reports.
\end{itemize}

\section{Selected Awards}
\begin{itemize}
    \item Third Prize in Huajiao Cup National College Student Mathematics Competition\hfill 2019
    \item Academic Excellence Awards\hfill 2020
    \item Outstanding Student Leaders (twice)\hfill 2021
\end{itemize}

\section{Skills}
\textbf{Programming Languages:} \small Python, C, Java, Matlab, Verilog (ranked by proficiency)

\textbf{Tools and Frameworks:} \small \LaTeX, PyTorch


\end{document}
